Type Refinements for the Working Class

### 2015-11-09 paper.tex
turn off no-cite
Add bob citations

The types of the semantic theory can then be said to \emph{refine} the types of
the syntactic theory, both by placing restrictions on membership and by
coarsening equivalence. Thus far, all developments of behavioral type theory
have been built on a \emph{unityped} syntactic framework, and so the relation
to type refinements has been difficult to see. In this paper, we contribute a
full theory of behavioral refinements over multi-sorted abstract binding trees,
a simple formal type theory \cite{harper:2016, sterling-morrison:2015}; this
hybrid system allows the deployment of a Nuprl-style type theory over any
signature of sorts and operators.

\ifdraft{}{
  \nocite{*}
  \bibliographystyle{abbrv}
  \bibliography{refs}
}

>>>>

The types of the semantic theory can then be said to \emph{refine} the types of
the syntactic theory \cite{harper-davies:2014, harper-duff:2015, harper:2016},
both by placing restrictions on membership and by coarsening equivalence. Thus
far, all developments of behavioral type theory have been built on a
\emph{unityped} syntactic framework, and so the relation to type refinements
has been difficult to see. In this paper, we contribute a full theory of
behavioral refinements over multi-sorted abstract binding trees, a simple
formal type theory \cite{harper:2016, sterling-morrison:2015}; this hybrid
system allows the deployment of a Nuprl-style type theory over any signature of
sorts and operators.

\ifdraft{}{
  \bibliographystyle{abbrv}
  \bibliography{refs}
}
